---
title: "Linear Models"
author: "Anna Ma"
date: "11/16/2021"
output: github_document
---

```{r, message = FALSE}
library(tidyverse)
library(p8105.datasets)
```

Load NYC Airbnb data

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>%
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(borough != "Staten Island") %>% 
  select(price, stars, borough, neighborhood, room_type)
```

Visualizations.. 

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price)) +
  geom_point()
```

Let's fit  a linear model (usually need to plot more and observe association between variables before actually fitting the regression)

```{r}
fit = lm(price ~ stars + borough, data = nyc_airbnb)

#we can also do summary(fit) to see more information about the regression 

#Putting the result in a dataframe: 
fit %>% 
  broom::tidy() %>% 
  mutate(term = str_replace(term, "borough", "Borough: ")) %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable()
```

## Diagnostics

Compare residuals and have result in a data frame

```{r}
modelr::add_residuals(nyc_airbnb, fit)
```

Graph the residual

```{r}
modelr::add_residuals(nyc_airbnb, fit) %>% 
  ggplot(aes(x = stars, y = resid)) +
  geom_point()
``` 

```{r}
modelr::add_residuals(nyc_airbnb, fit) %>% 
  ggplot(aes(x = resid)) +
  geom_density() + 
  xlim(-200, 200)
```


## Interactions? Nesting?
Let's try a different model

```{r}
fit = lm(price ~ stars * borough + room_type * borough, data = nyc_airbnb)

broom::tidy(fit)
```

let's try nesting ...

```{r}
nyc_airbnb %>% 
  relocate(borough) %>% 
  nest(data = price:room_type)
```

Now fit the model for each borough, and see how stars and room type affects each borough, map across the dataset

```{r}
nyc_airbnb %>% 
  relocate(borough) %>% 
  nest(data = price:room_type) %>% 
  mutate(
    lm_fits = map(.x = data, ~lm(price ~ stars+room_type, data = .x)),
    # map the "data" column in the dataframe to lm function, .x is a place holder, so in the function lm, everytime I see .x from the data colum and fit the lm function to it
    lm_result = map(lm_fits, broom::tidy)
    ) %>% 
  select(borough, lm_result) %>% 
  unnest(lm_result) %>% 
  # look at how stars affect the price across different boroughs 
  filter(term == "stars")
```

Look at neighborhoods in Manhattan ... 

```{r}
manhattan_lm_results_df = 
  nyc_airbnb %>% 
    filter(borough == "Manhattan") %>% 
    select(-borough) %>% 
    relocate(neighborhood) %>% 
    nest(data = price:room_type) %>% 
    mutate(lm_fits = map(.x = data, ~lm(price ~   stars+room_type, data = .x)),
           lm_results = map(lm_fits, broom::tidy)
           ) %>% 
    select(neighborhood, lm_results) %>% 
    unnest(lm_results)
```

Shows the density of the estimate of the impact of stars on price. Show the relationship between stars and price.

```{r}
manhattan_lm_results_df %>% 
  filter(term == "stars") %>% 
  ggplot(aes(x = estimate)) + 
  geom_density()
```

So, from the plot we can see that across the boroughs, increasing stars does not generally have that big of an effect. In some places it makes a big effect, +300, and in some places it makes things cheaper

```{r}
manhattan_lm_results_df %>% 
  filter(str_detect(term, "room_type")) %>% 
  ggplot(aes(x = neighborhood, y = estimate)) + 
  geom_point() + 
  facet_grid(~term) +
  ## ggplot x axis textrotate
  theme(axis.text.x = element_text(angle = 90, vjust = .5, hjust = 1))
```

interpretation:
In every neighborhood in Manhattan, I fit a linear regression of price against stars and room type. So, if i look at any of the points, that's the coefficient for room type(private or shared) in each neighborhood when I'm adjusting for stars. Keeping star rates fixed, going to a private room from entire home is gonna cost 100 dollar less per night for battery park city. This is relatively stable across all the neighborhood in Manhattan. 
The plot tells us what the effect is for each neighborhood, how much variability across neighborhoods, where u see bigger effects and where u see smaller effects. 