---
title: "Cross Validation"
author: "Anna Ma"
date: "11/19/2021"
output: github_document
---

```{r}
library(tidyverse)
library(modelr)
library(mgcv)
```


## Simulate a data set

```{r}
set.seed(1)

nonlin_df = 
  tibble(
    id = 1:100,
    x = runif(100, 0, 1),
    y = 1 - 10 * (x - .3) ^ 2 + rnorm(100, 0, .3)
  )

nonlin_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point()
```

## cross validation by hand

create splots by hand; plot; fit some model

```{r}
train_df = sample_n(nonlin_df, 80)
# select the exact 20 that is not in the 80 from above 
# anti join: look what is in the nonlin and in the train df 
test_df = anti_join(nonlin_df, train_df, by = "id")

ggplot(train_df, aes(x = x, y = y)) + 
  geom_point() + 
  geom_point(data = test_df, color = "red")
```

Fit my models:

```{r}
linear_mod = lm(y~x, data = train_df)
smooth_mod = mgcv::gam(y ~ s(x), data = train_df)
wiggly_mod = mgcv::gam(y ~ s(x, k = 30), sp = 10e-6, data = train_df)
```

Plot the result

```{r}
train_df %>% 
  add_predictions(smooth_mod) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point() + 
  geom_line(aes(y = pred), color = "red")
```

Quantify the results

```{r}
rmse(linear_mod, test_df)
rmse(smooth_mod, test_df)
rmse(wiggly_mod, test_df)
```

Get the 80-20 split again and test again -- iteration

## CV iteratively

Use `modelr::crossv_mc`

```{r}
#randomized 80-20 data set for 100 time, each time is a new set
cv_df = 
  crossv_mc(nonlin_df,100)

#we can conver it to tibble see what values are in each. 
cv_df %>%  pull(train) %>% .[[1]] %>% as_tibble()
```

```{r}
cv_df =
  cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
```

Let's fit some models

```{r}
cv_df = 
  cv_df %>% 
  mutate(
    linear_mod  = map(train, ~lm(y ~ x, data = .x)),
    smooth_mod  = map(train, ~mgcv::gam(y ~ s(x), data = .x)),
    wiggly_mod  = map(train, ~gam(y ~ s(x, k = 30), sp = 10e-6, data = .x))) %>% 
  mutate(
    rmse_linear = map2_dbl(linear_mod, test, ~rmse(model = .x, data = .y)),
    rmse_smooth = map2_dbl(smooth_mod, test, ~rmse(model = .x, data = .y)),
    rmse_wiggly = map2_dbl(wiggly_mod, test, ~rmse(model = .x, data = .y)))
```

look at output

```{r}
cv_df %>% 
  select(.id, starts_with("rmse")) %>% 
  pivot_longer(
    rmse_linear:rmse_wiggly,
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_boxplot()
```

## Realistic example

```{r}
child_growth = read_csv("nepalese_children.csv")
```

```{r}
child_growth %>% 
  ggplot(aes(x = weight, y = armc)) + 
  geom_point(alpha = .5)
```

weight change point for the change point model pwl_mod(piece wise linear model)
```{r}
child_growth =
  child_growth %>% 
  mutate(weight_cp = (weight > 7) * (weight - 7))
```

Consider candidate models

```{r}
linear_mod = lm(armc ~ weight, data = child_growth)
pwl_mod    = lm(armc ~ weight + weight_cp, data = child_growth)
smooth_mod = gam(armc ~ s(weight), data = child_growth)
```

plot

```{r}
child_growth %>% 
  gather_predictions(linear_mod, pwl_mod, smooth_mod) %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = weight, y = armc)) + 
  geom_point(alpha = .5) +
  geom_line(aes(y = pred), color = "red") + 
  facet_grid(~model)
```

cross validation

```{r}
cv_df =
  crossv_mc(child_growth, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
```

```{r}
cv_df = 
  cv_df %>% 
  mutate(
    linear_mod  = map(train, ~lm(armc ~ weight, data = .x)),
    pwl_mod     = map(train, ~lm(armc ~ weight + weight_cp, data = .x)),
    smooth_mod  = map(train, ~gam(armc ~ s(weight), data = as_tibble(.x)))) %>% 
  mutate(
    rmse_linear = map2_dbl(linear_mod, test, ~rmse(model = .x, data = .y)),
    rmse_pwl    = map2_dbl(pwl_mod, test, ~rmse(model = .x, data = .y)),
    rmse_smooth = map2_dbl(smooth_mod, test, ~rmse(model = .x, data = .y)))
```

plot the prediction error distribution for each candidate model.

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_boxplot()
```

